Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-07 paper/sec-mva.tex
Implemented comments from Nathan

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is specific of the analysis category: resolved, intermediate, or boosted.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the neural-network output, including in the final layer.
%
In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
  \vspace{-2cm}
  \caption{\small Architecture of the Artificial
    Neural Network
    used for the analysis of the
    boosted
    category, with $N_{\rm var}=21$ input variables and thus
    the same number of neurons
  in the first layer.
  %
  The color code in the neuron connections (the weights) is a heat map,
  with red indicating large values and black small values.
}
\label{fig:nnarch}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

 Therefore, the training of the neural networks consist on the
 minimization of the cross-entropy error,
 Eq.~(\ref{cross-entropy}), which in this work is achieved using a
 Genetic Algorithm.
 %
 The GA training is performed for a very large 
 number of generations, in this case $N_{\rm gen}=50k$, to avoid
 under-training.
 %
 We have verified that if a larger number of generations
 are used the results are unchanged.
 %
 We have also verified that using a cross-validation stopping
 criterion, in particular, the same one as
 that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}
 does not modify the results.
 %
 This cross-validation entails dividing the input MC dataset into two disjoint sets,
 and use one for the training and the other for the validation: the optimal
 stopping point is then indicated by the minimum of the error function
 Eq.~(\ref{cross-entropy}) for the validation sub-sample.

@@

  The ratio of energy correlation functions $C_2^{\beta}$ is defined as
  \be
  \label{eq:c2}
C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
\ee
while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
\be
e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
  \label{eq:d2}
D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
\ee
The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
  are sensitive to $N$-prong substructure.
  %
  The free parameter $\beta$ is set to a value of $\beta=2$,
  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
\end{itemize}
%
Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis,
17 for the semi-resolved, and 21 for the boosted category.
%
Given that the MVA is able to identify the most discriminatory variables
and to ignore those that have smaller effect, it is advantageous to
include as many substructure variables as possible.
%
This is one of the main advantages of ANNs in this context: they are inherently redundant, so
adding additional information, even if carries very little weight, will never degrade
the classification power of the MVA.

@@

The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve.
%
It is clear that we can achieve  high signal efficiency by using
a small value of the cut in the ANN output, but this choice will be
affected from a poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
The usefulness of ROC curves is that they allow to determine and
optimal cut value that removes enough background without degrading too much the signal efficiency.
%
Another important requirement on the value of $y_{\rm cut}$ is that
the  number of expected  signal events (the physical
events for a given integrated
luminosity, not the MC events used for the ANN training)
after the cut is large enough.

@@

As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
event with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$
we are still left
with around 100 events at the HL-LHC, which is a reasonable number,
which the background being reduced substantially to around
1000 events.
%
A similar cut would work fine for the intermediate category, though here
the backgrounds are much larger and thus the expected signal significance smaller.
%
For the resolved case, the signal significance would be only slightly
improved for any value of the cut.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \small
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Boosted category}\\
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.82$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
      1070   &  $7.6\cdot 10^5$    &  1.2    &  $1.4\cdot 10^{-3}$  & 790 & $2.2\cdot 10^4$ & 5.4  & 0.034\\
      \hline
      \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Intermediate category}\\
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.80$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
      670   &   $5.3\cdot 10^5$   &   0.9   &  $1.2\cdot 10^{-3}$ & 360  & $5.5\cdot 10^3$ & 4.8  & $0.06$ \\
      \hline
      \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Resolved category}\\
    \hline
      \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.65$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    $3700$   &   $1.5\cdot 10^{7}$   & 1.0     &  $3\cdot 10^{-4}$   & $1.3\cdot 10^{3}$ &
    $8.3\cdot 10^{4}$  & 4.5 & 0.01 \\
        \hline
  \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant, in the three categories, compared with the
    result of the cut-based analysis.
    %
    We indicate the number of signal and
    background events
    at the HL-LHC, as well as the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    The value of the ANN output cut $y_{\rm cut}$
    is optimised separately in the
    three categories.
    %
    The $y_{\rm cut}=0$ value corresponds to row C2 in Table~\ref{tab:cutflow_noPU_1}.
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The results of Fig.~\ref{fig:sb_mva}  show that
for all categories the  improvement in signal
significance arising from the MVA is substantial, growing from around 1
to around 5 in the three cases.
%
The optimal values of $y_{\rm cut}$ ensure that the
number of events at the HL-LHC is still well appreciable: we obtain
1300, 360 and 800 events in the resolved, intermediate, and
boosted categories respectively.
%
Therefore, thanks to the MVA, we predict that one should be able
to find evidence for the production of Higgs boson pairs
at the HL-LHC using the $4b$ channel alone.

Another important benefit of the MVA applied to the boosted
category is that fact that the background is substantially
reduced so that $S/B$ can be as large as 10\% for the optimal
values of the ANN output cut.
%
Note that this is not true for the other two categories,
where $S/B$ is roughly constant.
%
A reasonably large value of $S/B$ is beneficial
from the experimental point of view, since it indicates
that the measurement is feasible even if the
systematic uncertainties are not very small.

@@

In Fig.~\ref{fig:nnresponse_PU} we present
the distribution of the ANN output for the
signal and background MC events in the boosted and resolved categories --
the analogous comparison in the case without PU was shown
in Fig.~\ref{fig:nnresponse}.
%
We observe that the clear MVA discrimination
between signal and background events in the two categories is robust
when PU is included.
%
However, by comparing with Fig.~\ref{fig:nnresponse}, we see
that some of the most distinguishing features that separate signal
and background in the ANN output are reduced when PU effects
are included.
%
For instance, in the boosted category, there is a trend of the distribution
for signal events to move towards smaller values of the
ANN discriminant.
%
This in turn will entail a reduction of the signal significance as
compared to the case without PU.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
\includegraphics[width=0.49\textwidth]{plots/Resolved_disc_SKPU80.pdf}
\includegraphics[width=0.49\textwidth]{plots/Boosted_disc_SKPU80.pdf}
\caption{\small Same as Fig.~\ref{fig:nnresponse},
  this time with $\la n_{\rm PU}\ra=80$ PU events per bunch crossing
  and SK subtraction, for the resolved (left) and boosted
  (right) categories.
  %
  The corresponding comparison without PU was shown in
  Fig.~\ref{fig:nnresponse}.
}
\label{fig:nnresponse_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \small
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
    248     &   7250             &  2.9       & 0.034 \\
    \hline
       \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
  53  &  2547        & 1.1        &  0.02 \\
  \hline
  \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
  1123  &    $8.5\cdot 10^6$   & 0.25       &  $1.3\cdot 10^{-4}$       &
  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
        \hline
  \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowMVA} in the case
    of PU+SK, with $\la n_{\rm PU}\ra=80$.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is specific of the analysis category: resolved, intermediate, or boosted.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the neural-network output.
%
In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
  \vspace{-2cm}
  \caption{\small Architecture of the Artificial
    Neural Network (ANN)
    used for the analysis of the
    boosted
    category, with $N_{\rm var}=21$ input variables and thus
    the same number of neurons
  in the first layer.
  %
  The color code in the neuron connections (the weights) is a heat map,
  with red indicating large values and black small values.
}
\label{fig:nnarch}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

 Therefore, the training of the neural networks consist on the
 minimization of the cross-entropy error,
 Eq.~(\ref{cross-entropy}), which in this work is achieved using a
 Genetic Algorithm.
 %
 The GA training is performed for a very large 
 number of generations, in this case $N_{\rm gen}=50k$, to avoid
 under-training.
 %
 We have verified that if a larger number of generations
 are used the results are unchanged.
 %

 In order to avoid overfitting,
 we have used a cross-validation stopping
 criterion, in particular, the same one as
 that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}
 does not modify the results.
 %
 This cross-validation entails dividing the input MC dataset into two disjoint sets,
 and use one for the training and the other for the validation: the optimal
 stopping point is then indicated by the minimum of the error function
 Eq.~(\ref{cross-entropy}) for the validation sub-sample.

@@

  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
  \be
  \label{eq:c2}
C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
\ee
while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
\be
e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
  \label{eq:d2}
D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
\ee
The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
  are sensitive to $N$-prong substructure.
  %
  The free parameter $\beta$ is set to a value of $\beta=2$,
  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
\end{itemize}
%
Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the
resolved analysis,
17 for the intermediate,
and 21 for the boosted category.
%
Given that the MVA is able to identify the most discriminatory variables
and to ignore those that have smaller effect, it is advantageous to
include as many substructure variables as possible.
%
This is one of the main advantages of ANNs in this context: they are
inherently redundant, so
adding additional information, even if carries very little weight,
should not degrade
the classification power of the MVA (other than making the GA
minimization less efficient).

@@

The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve.
%
It is clear that we can achieve  high signal efficiency by using
a small value of the cut in the ANN output, but this choice will be
affected from a poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
Another important requirement on the value of $y_{\rm cut}$ is that
the  number of expected  signal events (the physical
events for a given integrated
luminosity, not the MC events used for the ANN training)
after the cut is large enough.

@@

As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
event with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$
we are still left
with around 100 events at the HL-LHC, 
which the background being reduced substantially to around
1000 events.
%
A similar cut would work fine for the intermediate category, though here
the backgrounds are much larger and thus the expected signal significance smaller.
%
For the resolved case, the signal significance would be only slightly
improved for any value of the cut.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1070 & $7.6\cdot 10^5$  & 1.2  & $1.4\cdot 10^{-3}$  \\
    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.034 \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 670   & $5.3\cdot 10^5$
    & 0.9 & $1.2\cdot 10^{-3}$ \\
    &  $y_{\rm cut}=0.80$ & 360  & $5.5\cdot 10^3$  & 4.8 & 0.06\\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 3700 &  $1.5\cdot 10^{7}$ &  1.0 &$3\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.65$ & 1300  & $8.3\cdot 10^{4}$ & 4.5 & 0.01 \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results $y_{\rm cut}=0$.
    %
    We indicate the number of signal and
    background events
    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    The pre-MVA results ($y_{\rm cut}=0$) corresponds to row C2 in
    Table~\ref{tab:cutflow_noPU_1}.
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The results of Fig.~\ref{fig:sb_mva}  show that
for all categories the  improvement in signal
significance arising from the MVA is substantial, growing from around 1
to around 5 in the three cases.
%
The optimal values of $y_{\rm cut}$ ensure that the
number of events at the HL-LHC is still well appreciable: we obtain
1300, 360 and 800 events in the resolved, intermediate, and
boosted categories respectively.
%
Another important benefit of the MVA applied to the boosted
category is that fact that the background is substantially
reduced so that $S/B$ can be as large as 10\% for the optimal
values of the ANN output cut.
%
Note that this is not true for the other two categories,
where $S/B$ is roughly constant.
%
A reasonably large value of $S/B$ is beneficial
from the experimental point of view, since it indicates
that the measurement is feasible even if the
systematic uncertainties are not very small.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 360   &  $1.4\cdot 10^6$ & 0.31   &
     $3\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.82$ &  250 & 7300  & 2.9    & 0.034  \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  150  & $9\cdot 10^5$    & 0.15    &
     $2\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.80$ & 50 & 2600  &  1.1   & 0.02 \\
    \hline
    \hline
    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  1100  & $8.5\cdot 10^6$
    & 0.25    &  $1.3\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.65$ & 430  & $3\cdot 10^4$  &  2.5   & 0.15  \\
    \hline
      \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
    of PU+SK, with $\la n_{\rm PU}\ra=80$.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-07 paper/sec-results.tex
Implemented comments from Nathan

The reason why the  $2b2j$ process
is not negligible as compared to the $4b$ component
is the following.
%
In the boosted category, for example,
the cross-sections at the C1e
level, that is, after the mass-drop tagging but before
$b$-tagging, is a factor 300 larger in the $2b2j$
sample as compared to the $4b$ sample.
%
Now, after $b$-tagging, the naive expectation would
be a suppression of the former by a factor $f_l^2 =10^{-4}$,
since a total of four $b$-tags are required to classify the
event as a Higgs candidate.
%
So the ratio of $2b2j$ over $4b$ should be
around $\simeq 3\%$.
  %
While  we have checked that this expectation is borne
out at parton level, before showering,
we find that  when parton shower effects
are accounted for, due to the radiation of $b\bar{b}$ pairs from the
light jets as well as due to combinatorics, the
number of  $b$ quarks in the  final state is
increased substantially in the $2b2j$ component as compared
to the parton level content,
enhancing the signal efficiency and making
it comparable to the $4b$ component.

>>>>

The reason why the  $2b2j$ process
is not negligible as compared to the $4b$ component
is the following.
%
In the boosted category, for example,
the cross-sections at the C1e
level, that is, after the mass-drop tagging but before
$b$-tagging, is a factor 300 larger in the $2b2j$
sample as compared to the $4b$ sample.
%
Now, after $b$-tagging, the naive expectation would
be a suppression of the former by a factor $f_l^2/f_b^2 =3\cdot 10^{-4}$,
since a total of four $b$-tags are required to classify the
event as a Higgs candidate.
%
So the ratio of $2b2j$ over $4b$ should be
around $\simeq 3\%$.
  %
While  we have checked that this expectation is borne
out at parton level, before showering,
we find that  when parton shower effects
are accounted for, due to the radiation of $b\bar{b}$ pairs from the
light jets as well as due to combinatorics, the
number of  $b$ quarks in the  final state is
increased substantially in the $2b2j$ component as compared
to the parton level content,
enhancing the signal efficiency and making
it comparable to the $4b$ component.

We can make this statement more quantitative in the following way.
%
To first approximation, and neglecting the contribution from charm mistags, the
overall efficiency of the $b$-tagging requirements in the resolved category will be
given by the following expression:
\be
\label{btaggingeff}
{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
\ee
with $n^{\rm (b-jet)}_j$ the fraction of events, satisfying all the selection cuts,
where $j$ jets, out of the leading four jets, of the event contain $b$ quarks (with $p_T^b\ge 15$
GeV).
%
Similar expressions can be derived to the boosted and intermediate categories.
%
The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
%
This leads to a ratio of overall $b$-tagging selection efficiencies
\be
\label{eq:naive}
\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
  \simeq
 \lp \frac{f_l}{f_b}\rp^2 \simeq 1.6\cdot 10^{-4} \, .
\ee
However, the actual situation is more complicated.
%
First of all, we will have a non-negligible fractions $n^{\rm (b-jet)}_j$
with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
during the shower.
%
Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
due to a combination of selection cuts and
parton shower effects.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \small
  \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
  \multicolumn{2}{|c|}{}   &  $n^{\rm (b-jet)}_0$  &  $n^{\rm (b-jet)}_1$  &  $n^{\rm (b-jet)}_2$  & $n^{\rm (b-jet)}_3$ &
    $n^{\rm (b-jet)}_4$ & ${\rm EFF}_{\rm b-tag}$ \\
    \hline
    \hline
    Signal  &  $hh\to 4b$  &   0.1\%    & 3\%     &  25\%     & 53\%     & 20\%      & 8.5\%  \\
    \hline
    \multirow{3}{*}{Background}  &  QCD $4b$  & 1\%      &  8\%    &   27\%   &  44\%     & 20\%       &  8.4\% \\
     &  QCD $2b2j$  &   9\%    & 42\%     &  49\%    & 1\%     &  0.1\%     & 0.04\%  \\
    &  QCD $4j$  &   96\%    &  3.5\%     & 0.5\%     &  0.01\%    & $3\cdot 10^{-4}$\%      &
    $2\cdot 10^{-4}$\%\\
    \hline
  \end{tabular}
  \caption{\small
    The relative fractions  $n^{\rm (b-jet)}_j$ of events for the resolved selection
    for which, out of the four leading small-$R$ jets, $j$ jets
    contain at least one $b$-quark with $p_T^b\ge 15$ GeV,
    both for signal events and for the three QCD background samples.
    %
    The last column indicates the overall predicted
    selection efficiency of the $b$-tagging procedure,
    Eq.~(\ref{btaggingeff})
    \label{tab:btaggingcheck}
  }
  \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Table~\ref{tab:btaggingcheck} we collect
the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
%
Therefore, we find that, rather than the estimate Eq.~(\ref{eq:naive}),
the correct ratio of $b$-tagging selection efficiencies is instead
\be
\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
  \ee
  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
    %
    This explains why the $2b2j$ contribution cannot be neglected as compared
    to the irreducible $4b$ component of the QCD background.
    %
    A similar calculation from the numbers of Table~\ref{tab:btaggingcheck} shows
    that, on the other hand, the $4j$ component of the background can safely
    be neglected.

%
